% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{fraguilarcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Fernando R. Aguilar}
\address{Brasilia, Federal District \linebreak Brazil}
\contacts{(+55 61) 99906-0320 \linebreak fernando@aguilar.net.br \linebreak www.fraguilar.com}

\begin{document}

	% Print the header
	\makeheader

	% Print the content of employments
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer, Intern}{Brazilian Space Agency}{(01/2017 - Present)}
			\begin{itemize}
				\item Responsible for maintaining and troubleshooting the internal human resources system.
                \item Evolved my organization, solution-oriented skills and ability to work alone after given instructions.
				\item Introduced to TDD paradigm, learned the importance of both writing and running unit tests. 
                \item Suggested small changes and improvements in the recently implemented scrum methodology.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Full-Stack Developer}{Energy Monitoring - UnB}{(06/2016 - 12/2016)}
			\begin{itemize}
                \item Designed and developed a system to monitor electric energy interpreters in university facilities.
                \item Understood the importance and best practices on writing a good documentation.
                \item Learned to be collaborative and to dissolve the group's lack of motivation.
                \item Solved recurrent configuration problems by applying some DevOps concepts.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Developer, Intern}{UeBrasil - Mahvla}{(12/2015 - 04/2016)}
			\begin{itemize}
				\item Worked on a scrum team to maintain and evolve electronic ankles 								monitoring system.
                \item Refactored some core functions, reducing complexibility and scaling new 						contracts.
                \item Helped on critical requirements analysis by suggesting measurable goals 						and making prototypes;
			\end{itemize}
		\end{cvsubsection}
        
	%Print the content of eductations%
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Brasilia, DF}{University of Brasília (UnB)}{(06/2014 - Present)}
			\begin{itemize}
				\item B.S.E. in Software Engineering, with minor in Electronic Engineering.
				\item \textbf{Coursework:} {Software Developing Processes \& Methodologies; Software Configuration Management;  Requirements Engineering; 3D modeling; Operating Systems; Human-computer interaction; Electronic Games; Technical Design; Fundamentals of computing; ... ;}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
    
	%Print the content of technical Experience%
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects:}{}{}
			\begin{itemize}
            	\item \textbf{Game Developing (2017):} Member on a cross-functional team. Constructing the Game Engine \& storyline. Managing, leading and interpreting ideas. [ C++, SDL 2 ]
				\item \textbf{Scientific Research (2017):} Modeling and analyzing concepts of Hofstadter's recursive functions using genetic algorithms. Orienter: Dr. Ronni Amorim.
                \item \textbf{Game Developing (2016):} Implemented a 'not so ordinary' Brick Breaker game. [ Unity, C\# ]
                \item \textbf{Solidaridad Charitable Portal (2016):} Informational and eCommerce platform to help local beneficent entities sell their handicrafts and get visibility. [ JS(Meteor) ]
                \item \textbf{Meteorological Station (2015):} Constructed a meteorological home station and an android app to check climate data. [ Arduino, Android SDK ]
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
    
    %Print the content of languages and technologies%
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf {Programming:} Python, Java, C, C++, JavaScript (Node.Js, Meteor), PHP, C\#, Shell;
				\item \textbf {Graphical Design:} Gimp, Unity, Inkscape, Catia, Photoshop, AutoCAD, Blender;
                \item \textbf{Web Development:} JavaScript (Angular, JQuery), HTML \& CSS, Ruby on Rails, Bootstrap, WordPress; 
                \item \textbf{Software Technologies:} Git, Docker, Gulp, Trevis CI, Jenkins, Vagrant, Puppet, Chef, Cucumber.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{cvsection}
\end{document}
