% The font could be set to Windows-specific Calibri by using the 'calibri' option
\title{CV - English}
\documentclass[]{fraguilarcv}

% For brazilian accentuation
\usepackage[brazilian]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% For mathematical symbols
\usepackage{amsmath}

% Header Personal Data
\name {Fernando R. Aguilar}
\address {Brasília, Brazil \linebreak 20, Male, Single}
\contacts {(+55 61) 999.060.320 \linebreak fernando@aguilar.net.br \linebreak @fraguilar}

\begin{document}

% Print the header
\makeheader

% Print the content of employments
\begin{cvsection}{Experience}
	\begin{cvsubsection}{Internship}{Medialab/UnB}{(06/2017 - Currently)}
		\begin{itemize}
			\item \textbf{Description:} Interdisciplinary research laboratory devoted to projects at the convergence of technology, multimedia, sciences, art and design.
			\item \textbf{Activities:} To change the ways of how humans and technologies interact. Monitored the exposition (\#16 ART: Artis intelligentia) and co-authored some projects exposed in Brazil and Portugal.
			\item \textbf{Learnings:} The value of putting in motion the creative potential. Experiencing the personal development consciously being present on daily interactions and reflections.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Internship}{Brazilian Space Agency}{(01/2017 - 05/2017)}
		\begin{itemize}
			\item \textbf{Description:} Technological division in charge of attending the organization that coordinates the Brazilian aerospace policies.
			\item \textbf{Activities:} Responsible for maintaining and troubleshooting the internal human resources system. Suggested improvements in the methodology design.
			\item \textbf{Learnings:} Evolved my personal organization, solution-oriented skills and ability to work alone after given instructions.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Developer}{Energy Monitoring System/UnB}{(06/2016 - 12/2016)}
		\begin{itemize}
			\item \textbf{Description:} System that provides real time information on how much energy a facility of the university is consuming.
			\item \textbf{Activities:} Developed new functionalities on the software. Solved recurrent configuration problems applying devops techniques.
			\item \textbf{Learnings:} The value of mediation and collaboration in a group.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Internship}{UeBrasil - Mahvla Group}{(12/2015 - 06/2016)}
		\begin{itemize}
			\item \textbf{Description:} Web system to control and monitor the status of electronic ankles used by the prison system.
			\item \textbf{Activities:} Evolved and refactored some important functionalities, improving the code metrics and reducing the cyclomatic complexity.
			\item \textbf{Learnings:} The whole process of making a single change in a critical software.
		\end{itemize}
	\end{cvsubsection}

	%Print the content of eductations%
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Gama, Brasilia, DF}{Universidade de Brasília (UnB)}{(06/2014 - Present)}
			\begin{itemize}
				\item Graduation in Software Engineering
				\item \textbf{Coursework:} {Software Developing Processes \& Methodologies; Configuration Management; Requirements Engineering; GameDev \& Design; Operating Systems; Human-computer interactions; ...}
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	%Print the content of technical Experience%
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Personal Projects:}{}{}
			\begin{itemize}
				\item \textbf{MaisMorra Game (2017):} Game made in 'Epic Game Jam'. Winner of Regionals, proceeding to the finals in Rock in Rio 2017. Allowed in-depth knowledge on Team Management, Art, Programing, Digital Marketing \& Business.
				\item \textbf{Portal Solidaridad (2016):} Platform that aims to provide financial freedom for charitable organizations and partners (solidaridad.com.br).
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{cvsection}

\end{document}
